\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-12 paper/experiments.tex
paper: edit loss section and rearrange related work
paper: more todos
paper: cleaned up more todos

To evaluate the performance of our system, we generated plans for queries on two data sets: the American Community Survey and a synthetic dataset.
\subsection{Data sets}

@@

\begin{figure}
  \centerfloat
  \input{queries}
  \caption{The queries used in our experiments.}
  \label{fig:queries}
\end{figure}

\begin{figure}
  \centerfloat
  \input{runtimes}
  \caption{Running time and error for queries with different imputation levels.}
  \label{fig:experiments}
\end{figure}

Figure~\ref{fig:experiments} provides a summary of our experimental results. For purposes of simplicity, we present only the results associated with
queries that return a result size matching our base case. This addresses the fact that deriving a reasonable error metric for set-queries 
is inherently task specific (e.g. consider tuning precision vs. recall). Meanwhile, for all queries that match, we apply a simple sum of errors squared
(SSE). Figure~\ref{fig:experiments} indicates the query number and the error produced by a query engine with traditional SQL null semantics (base error).
For imputations, we present two extremes of the $\alpha$ parameter: 0 and 1, which reflect a a focus on runtime and information loss, respectively.
For each query, the table displays the new error ($\epsilon$), the planning time ($t_p$) and the running time ($t_r$) in seconds.

The overall low planning times highlight the practicality of our algorithm, despite the exponential complexity. Runtimes clearly vary based on $\alpha$, allowing
users to tune their query performance as desired.

@@

Finally, we performed CERT imputation on the entirety of the ACS table, in order to compare our system to the traditional, pre-processing approach to imputation.
We note that the latter took \todo{add time}, compared to our maximum of \todo{add time}. Given the varying needs of database users, \ProjectName{} clearly allows flexibility without
a significant performance hit.

>>>>

To evaluate the performance of our system, we generated plans for queries on two data sets: the American Community Survey and a synthetic dataset.
\subsection{Data sets} \label{subsec:datasets}

@@

\todo{fix query references}
\begin{table}
  \centerfloat
  \input{queries}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table}

\begin{table}
  \centerfloat
  \input{runtimes}
  \caption{Running time and errors (SSE) for queries with different imputation levels. base error corresponds to the
error with traditional SQL null semantics. The errors for \ProjectName{} plans are labeled with $\epsilon$. The two
$\alpha$ levels reflect a relative focus on information loss. $t_p$ and $t_r$ represent planning and run time, respectively, in seconds.}
  \label{fig:experiments}
\end{table}

Figure~\ref{fig:experiments} provides a summary of our experimental results. For purposes of simplicity, we present only the results associated with
queries that return a result size matching our base case. This addresses the fact that deriving a reasonable error metric for set-queries 
is inherently task specific (e.g. consider tuning precision vs. recall). For all other queries, we use sum of squared errors (SSE) as a metric.
The overall low planning times highlight the practicality of our algorithm, despite the exponential complexity. Runtimes clearly vary based on $\alpha$, allowing
users to tune their query performance as desired.

@@

Finally, we performed CE-CART imputation on the entirety of the ACS table, in order to compare our system to the traditional, pre-processing approach to imputation.
We note that the latter took \todo{add time}, compared to our maximum of \todo{add time}. Given the varying needs of database users, \ProjectName{} clearly allows flexibility without
a significant performance hit.
